\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-08 paper/draft.tex
Checkpoint

\heading{Results}
% TODO \nv{Need to change terminology in plots---files should be (attempted) parallelism, name benchmark, cat should be merge.}
Fig.~\ref{fig:microbenchmarks} presents \sys's speedup as a function of \ttt{width=}2--64.
% (Bi-grams-opt is shown as the \ttt{opt} line in Fig.~\ref{fig:microbenchmarks}'s Bi-grams.)
Average speedups of the optimized \sys, \ie \ttt{eager} and \ttt{split} enabled, for \ttt{width=}\{2, 4, 8, 16, 32, 64\} are \todo{1.97, 3.5, 5.78, 8.83, 10.96, and 13.47}, respectively.
Average speedups for No Eager, \ie only \sys' transformations without its runtime support, are 1.63, 2.54, 3.86, 5.93 7.46 9.35$\times$.
% and the geometric means are 1.92, 3.39, 5.48, 7.94, 8.86, 8.51.}
% \kk{For the one-liners where split doesn't provide any benefit (or overhead) we don't show the PaSh w/o split line.}
% we experiment with a $200\times$ level of parallelism to see potential overheads
Tab.~\ref{tab:eval} shows that \sys's compilation time is negligible. % ($<5s$)
Filter and Bigrams-opt are not in Fig.~\ref{fig:microbenchmarks}, for which \sys achieves a speedup 1.5--2.5$\times$ and $30\times$.
\sys achieves a COST~\cite{mcsherryscalability} of 2 for all benchmarks.
%   size grows due to the resulting complexity of coordinating among parallel executions---multiple FIFOs per pipeline stage, merging and splitting, encoding of divide-and-conquer synchronization \etc
% The first number alone is interesting, as it captures \sys's output for the sequential script.
% As there is no parallelism involved, it highlights the initial (bare minimum) cost corresponding to using \sys.
% % this is the size of 
% This change in size does not necessarily translate to observed runtime, as most of the size increase comes from the setup and teardown of FIFOs responsible for interprocess (IPC) communication.
% FIFOs are simply pipes made explicit;
%   the performance characteristics, including in-kernel buffering and synchronization mechanisms, are identical between the two.

%   Two types of pairs where x y z coincide
%   - \sys adds no split, whenever whenever the DFG width is constant for the entire pipeline. In these cases the blue line is identical to the red line, which not shown.
%    Conversely, whenever both blue and red lines are shown, split nodes are needed due to changes in the pipeline width and result in performance improvements.
% 
%   - without split, the script is sequential (spell, bigrams)
% Early on they have a pure or no parallelizable pure
% and thus introduce an aggregator resulting in width of 1 right after, and requires a split.
% Thus, any configuration that does not has \ttt{split} is practically sequential beyond that point---\ie No Eager, Blocking Eager, and \sys w/o Split see no speedup.
% 
% Blocking eager: data parallelism, but no task parallelism
% No eager: blocking FIFO does not allow pushing -> underutilize CPU
% 
% The reason why Blocking Eager is usually slower than No Eager is due to \ttt{agg}regators that read multiple input streams at the same time---such \ttt{sort -m}.
% 
% Sort-sort possibly shows the full spectrum:
%   (iii) \sys's \ttt{eager} offers benefits despite the lack of \ttt{split} because it fully parallelizes the first \ttt{sort} while maintaining task parallelism
%   (iv) \sys gets full benefits because \ttt{split}ting allows parallelizing the second \ttt{sort} too.

  % Configurations where the parallel script produced is identical to an existing configuration are not shown.

@@

>>>>

\heading{Results}
% TODO \nv{Need to change terminology in plots---files should be (attempted) parallelism, name benchmark, cat should be merge.}
Fig.~\ref{fig:microbenchmarks} presents \sys's speedup as a function of \ttt{width=}2--64.
% (Bi-grams-opt is shown as the \ttt{opt} line in Fig.~\ref{fig:microbenchmarks}'s Bi-grams.)
Average speedups of the optimized \sys, \ie with \ttt{eager} and \ttt{split} enabled, for \ttt{width=}\{2, 4, 8, 16, 32, 64\} are \{\todo{1.97, 3.5, 5.78, 8.83, 10.96, 13.47}\}$\times$, respectively.
For No-Eager, \ie for only \sys' transformations without its runtime support, speedups drop to 1.63, 2.54, 3.86, 5.93 7.46 9.35$\times$.
% and the geometric means are 1.92, 3.39, 5.48, 7.94, 8.86, 8.51.}
% \kk{For the one-liners where split doesn't provide any benefit (or overhead) we don't show the PaSh w/o split line.}
% we experiment with a $200\times$ level of parallelism to see potential overheads

Configurations where the parallel script produced is identical to an existing configuration are not shown.
There are two types of such cases (that appear in \todo{four} plots).
In the first, blue and red (not shown) lines are identical when \sys adds no \ttt{split} because the DFG width is constant for the entire pipeline;
  conversely, if both blue and red lines are shown, \ttt{split}s are needed due to changes in the pipeline width and result in performance improvements.
In the second type, the script features a command in \pur that introduces an aggregator resulting in width of 1 right after, needing a \ttt{split} to regain width.
Non-\ttt{split} configurations are sequential beyond that aggregator---\ie No Eager, Blocking Eager, and \sys w/o Split see no speedup and are identical (\todo{spell, bigrams}).

Tab.~\ref{tab:eval} shows that \sys's compilation time is negligible. % ($<5s$)
Filter and Bigrams-opt are not in Fig.~\ref{fig:microbenchmarks}, for which \sys achieves an average speedup 1.5--2.5$\times$ and $30\times$.
\sys achieves a COST~\cite{mcsherryscalability} of 2 for all benchmarks.
%   size grows due to the resulting complexity of coordinating among parallel executions---multiple FIFOs per pipeline stage, merging and splitting, encoding of divide-and-conquer synchronization \etc
% The first number alone is interesting, as it captures \sys's output for the sequential script.
% As there is no parallelism involved, it highlights the initial (bare minimum) cost corresponding to using \sys.
% % this is the size of 
% This change in size does not necessarily translate to observed runtime, as most of the size increase comes from the setup and teardown of FIFOs responsible for interprocess (IPC) communication.
% FIFOs are simply pipes made explicit;
%   the performance characteristics, including in-kernel buffering and synchronization mechanisms, are identical between the two.

@@

Blocking eager: data parallelism, but no task parallelism
No eager: blocking FIFO does not allow pushing -> underutilize CPU

The reason why Blocking Eager is usually slower than No Eager is due to \ttt{agg}regators that read multiple input streams at the same time---such \ttt{sort -m}.

Sort-sort possibly shows the full spectrum:
  (iii) \sys's \ttt{eager} offers benefits despite the lack of \ttt{split} because it fully parallelizes the first \ttt{sort} while maintaining task parallelism
  (iv) \sys gets full benefits because \ttt{split}ting allows parallelizing the second \ttt{sort} too.
